Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex

% SJT - the "i" and "t" subscripts here look a bit odd: is that what's intended?
\noindent 
\begin{equation}
\ident{riskfactor}_{i}{}_{t}=O_{\footnotesize\ident{rf}}(i,t)
\end{equation}
\noindent
In the case of the Cardano blockchain, these values are usually
provided through an \emph{oracle} mechanism\cite{oracles}. An oracle
could be a trusted party providing necessary data or network of parties
under consensus {[}find a reference{]}. 
% SJT REF needed
From a Marlowe DSL perspective,
the exact mechanism that provides external data is less important,
as Marlowe abstracts over IO by requiring a particular type of input -- a 
\texttt{Choice} -- that is protected with a cryptographic signature by the source of the choice.
% SJT changed from "owner" to "source".
As a result, the event of receiving data from an oracle is treated the
same as receiving numeric input in other languages

@@

ACTUS is defined in a textual specification\footnote{Available from \url{https://www.actusfrf.org/techspecs}.} which, while expressed in mathematical notation, is essentially informal. In this section we describe how this specification is turned into an \emph{executable} version by rendering it in Haskell. This translation is in fact a transliteration, since notation, variable names and so forth are respected.
% SJT: are you happy with this? If not, let's rephrase,
% but it would be good include something to this effect.

@@

% SJT - do you mean \mapsto or \rightarrow here?
\noindent 
\begin{equation}
\ident{Applicability}:\ident{ContractTerms}\mapsto \ident{Bool}
\end{equation}

ACTUS defines a family of applicability functions polymorphic on contract
type (TODO link to ACTUS applicability):
% SJT something needed here.

\smallskip
% SJT changed ContractTerm to ContractTerms
\noindent 
\begin{equation}
\ident{Applicability} : \ident{ContractType} \times \ident{ContractTerms} \mapsto \ident{ApplicabilityType}
\end{equation}
\noindent
where applicability could be: \emph{none}, \emph{always}, \emph{nullable}, or \emph{multiple}.

@@

\noindent 
\begin{equation}
\ident{adjusted}=\ident{max(min(original,floor),cap)}
\end{equation}
\noindent
We addressed this issue by introducing the \texttt{Cond} expression construct in order
to represent conditional expressions, rather than only conditional contracts as was the case before. Instead of using the \texttt{If}
contract to decide the value of some variable, we use a conditional expression instead.  
\texttt{Cond} is  a pure function
that returns a value depending on a condition, in contrast to the \texttt{If}
contract that chooses between two continuation contracts. 
% SJT I don't think we need to say this.
%The name is borrowed from a similar function in Lisp.

@@

% SJT changed title from {Comparison with existing smart-contracts approaches }
% it's traditional to call this "relatyed work".

>>>>

% SJT - the "i" and "t" subscripts here look a bit odd: is that what's intended?
% dk14 - fixed
\noindent 
\begin{equation}
\ident{riskfactor}_{it}=O_{\footnotesize\ident{rf}}(i,t)
\end{equation}
\noindent
In the case of the Cardano blockchain, these values are usually
provided through an \emph{oracle} mechanism\cite{oracles}. An oracle
could be a trusted party providing necessary data or network of parties
under consensus \cite{de-oracles}. 
% SJT REF needed
% dk14. I've found this one has explanation for oracles (ChainLink etc)

From a Marlowe DSL perspective,
the exact mechanism that provides external data is less important,
as Marlowe abstracts over IO by requiring a particular type of input -- a 
\texttt{Choice} -- that is protected with a cryptographic signature by the source of the choice.
% SJT changed from "owner" to "source".
% dk14 OK
As a result, the event of receiving data from an oracle is treated the
same as receiving numeric input in other languages

@@

ACTUS is defined in a textual specification\footnote{Available from \url{https://www.actusfrf.org/techspecs}.} which, while expressed in mathematical notation, is essentially informal. In this section we describe how this specification is turned into an \emph{executable} version by rendering it in Haskell. This translation is in fact a transliteration, since notation, variable names and so forth are respected.
% SJT: are you happy with this? If not, let's rephrase,
% but it would be good include something to this effect.
% dk14 thanks for adding this

@@

% SJT - do you mean \mapsto or \rightarrow here?
% dk14 - it is a mapping, but could be function/morphism too
\noindent 
\begin{equation}
\ident{Applicability}:\ident{ContractTerms}\rightarrow \ident{Bool}
\end{equation}

ACTUS standard defines a family of applicability functions polymorphic on contract
type:
% SJT something needed here.
% dk14 - we already gave a link to actusfrf, so I think I can skip references

\smallskip
% SJT changed ContractTerm to ContractTerms
\noindent 
\begin{equation}
\ident{Applicability} : \ident{ContractType} \times \ident{ContractTerms} \rightarrow \ident{ApplicabilityType}
\end{equation}
\noindent
where applicability could be: \emph{none}, \emph{always}, \emph{nullable}, or \emph{multiple}.

@@

\noindent 
\begin{equation}
\ident{adjusted}=\ident{max(min(original,floor),cap)}
\end{equation}
\noindent
We addressed this issue by introducing the \texttt{Cond} expression construct in order
to represent conditional expressions, rather than only conditional contracts as was the case before. Instead of using the \texttt{If}
contract to decide the value of some variable, we use a conditional expression instead.  
\texttt{Cond} is  a pure function
that returns a value depending on a condition, in contrast to the \texttt{If}
contract that chooses between two continuation contracts. 
% SJT I don't think we need to say this.
%The name is borrowed from a similar function in Lisp.
% dk14 - Oh sure. I was going to remove it too :)

@@

% SJT changed title from {Comparison with existing smart-contracts approaches }
% it's traditional to call this "relatyed work".
% dk14. sure this is better
